Summary Tables ITHIMR

### 2019-05-01 summary_tables_PA_AP.Rmd

dist_scen<- io[[cities[x]]]$trip_scen_sets %>% group_by(trip_mode, scenario) %>% summarise(sum(trip_distance))
dist_scen<- as.data.frame (dist_scen)
names(dist_scen)[3]<-"distance"
dist_scen<-spread(dist_scen, trip_mode, distance)
dist_scen$sum<-rowSums (dist_scen[2:(ncol(dist_scen)-1)], na.rm = FALSE, dims = 1)
dist_scen_prop<- round(dist_scen[,2:(ncol(dist_scen)-1)]*100/dist_scen$sum, digits=1)
dist_scen_prop<- cbind(dist_scen[,1], dist_scen_prop)

names(dist_scen_prop)[1]<-"Scenario"
dist_scen_prop$Scenario<- c("baseline","walk_scen", "bike_scen", "car_scen", "MC_scen", "bus_scen")
print (as.character(cities[x]))
print(dist_scen_prop)
#library(knitr)
#library(kableExtra)
#kable(dist_scen_prop)
}
```

>>>>

dist_scen<- io[[cities[x]]]$trip_scen_sets %>% group_by(trip_mode, scenario) %>% summarise(sum(trip_distance))
dist_scen<- as.data.frame (dist_scen)
names(dist_scen)[3]<-"distance"
dist_scen<-spread(dist_scen, trip_mode, distance)

dist_scen$sum<-rowSums (dist_scen[2:(ncol(dist_scen)-1)], na.rm = FALSE, dims = 1)
dist_scen_prop<- round(dist_scen[,2:(ncol(dist_scen)-1)]*100/dist_scen$sum, digits=1)
dist_scen_prop<- cbind(dist_scen[,1], dist_scen_prop)

names(dist_scen_prop)[1]<-"Scenario"
dist_scen_prop$Scenario<- c("baseline","walk_scen", "bike_scen", "car_scen", "MC_scen", "bus_scen")
print (as.character(cities[x]))
print(dist_scen_prop)
print(dist_scen)
#library(knitr)
#library(kableExtra)
#kable(dist_scen_prop)
}
```
